Matching and merging high-resolution and legacy seismic images

### 2018-04-30 chapter-locfreq/paper.tex
thesis and presentation

\begin{abstract}
        Seismic data can experience non-stationary frequency variations caused by attenuation. 
        This problem is encountered when matching multiple data sets, such as in multicomponent image registration, because signals with differing frequency content are hard to correlate. 
        In this chapter, we introduce two methods for balancing frequency content between data sets while taking into account non-stationary frequency variations. 
        Both methods involve finding and applying a non-stationary smoothing operator to minimize the local frequency difference between data sets. 
        Numerical examples demonstrate that the proposed method improves multicomponent image registration and matching images of differing resolution. 
\end{abstract}

\section{Introduction}
        Matching seismic data has many applications in geophysical processing methods, such as multi-component image registration, time-lapse image registration, matching well-ties to seismic data, and merging seismic data sets \cite[]{ps,fomel2003,lumley,herrera2012}.
        Typically, the workflow for matching data involves finding the optimal time shift, or amount of stretching and compressing, of one trace relative to the other that produces the greatest similarity between the two traces, as seen in dynamic time warping and local similarity scanning \cite[]{hale2013, timelapse, herrera}. 
        However, when the two signals that need to be aligned have different spectral content, their comparison can be difficult. 
        Most seismic data experience non-stationary, or spatially and temporally variant, frequency content caused by attenuation. 
        This problem was discussed in application to multicomponent image registration by \cite{fomel2003}, who applied frequency balancing methods to improve registration results. 
        \cite{ltft} proposed using local time-frequency decomposition (LTFD) to balance frequencies between multicomponent data during registration. 
        However, LTFD is a relatively computationally expensive method.

        In this chapter, we propose methods for removing non-stationary frequency differences that limit the effectiveness of matching data. 
        We suggest applying the either of the proposed methods to processing flows that involve matching data before attempting to find the time shift to align their signal content. 
        To balance frequency content, we use a non-stationary smoothing operator with an adjustable smoothing radius to apply to the higher frequency data set. 
        Our first approach finds the smoothing operator directly, but is based on the primary assumption that the data can be modeled by a summation of Ricker wavelets. 
        Our second approach of finding the smoothing radius is based on understanding what the smoothing operator physically does, and takes the form of an optimization problem which is solved using an iterative method. 
        We introduce these methods and apply them to examples of merging high-resolution and conventional seismic images and multicomponent image registration.

@@

        In order to balance local frequency content, we propose smoothing the higher frequency data using a non-stationary triangle smoothing operator with an adjustable radius. 
        Here, the radius at each point is the number of samples in time that that specific data point gets averaged over in a triangle weight.

        In order to find the temporally and spatially variable smoothing radius that we need to apply to the higher frequency image to balance local frequency content with the lower frequency image, we take two approaches.
        The first approach is finding the smoothing radius based on assumptions of what the data we are looking at can be represented by, and the second approach is based on understanding physically what non-stationary smoothing does to a data set.
        Both approaches work well in different situations---the first approach is less computationally expensive than the second approach, but is only applicable when the two data sets fit the assumptions that are used to calculate what the smoothing radius is.
        The second approach finds the smoothing radius in an iterative manner, but manages to work well for any data set given to it.

@@

        This method is based off of the primary assumption that the signal can be represented by Ricker wavelets convolved with the Earth's reflectivity series.
        Since the data we are working with are seismic, this can be a good assumption \cite[]{ricker}.

@@

        We measure local frequencies in both images and apply smoothing specified by equation~(\ref{eq:radius}) to the high-resolution image.
        Since this is only an approximation of what the smoothing radius should be under ideal conditions, we adjust the constant $12$ in the equation to achieve a better match. 
        In this example, this effectively reduces the difference between the spectral content of the images, as shown in Figure \ref{fig:hires-smooth-spec}. 
        Figure \ref{fig:freqdif,freqdif-filt} shows the difference in local frequencies before and after smoothing. 
        After smoothing, the frequency difference is minimized.

@@

        \subsection{Iterative method for calculating the smoothing radius}
        \inputdir{merge}
        The theoretical smoothing radius works in some situations, like in the first example of the next chapter, but it doesn't work in situations where there is not much overlap in frequency content between data sets, like in the second example of the next chapter.
        In this case, we use an iterative method to find what the smoothing radius should be that is based on the physical understanding of what smoothing is doing.

        The goal of this method is to find the temporally and spatially variable smoothing radius, $\mathbf{R}$, that minimizes the difference in local frequencies between the two data sets. 
        This can be shown in the objective function
        \begin{equation}
                \label{eq:obj}
                \min_{\mathbf{R} \in [1,N]} \Big \Vert \mathbf{F}[ \mathbf{S}_{\mathbf{R}} \mathbf{d}_h ] - 
                \mathbf{F}[ \mathbf{d}_l] \Big \Vert\;,
        \end{equation}
        where $\mathbf{S}_\mathbf{R}$ is the non-stationary smoothing operator of smoothing radius $\mathbf{R}$, $\mathbf{d}_h$ is the higher frequency data, $\mathbf{d}_l$ is the lower frequency data, $\mathbf{F}$ is the local frequency operator, and $N$ is the maximum size of the smoothing radius.
        Although smoothing is a linear operation, the smoothed data, $\mathbf{S_R d}_h$, depends non-linearly on $R$. However, the objective from equation (\ref{eq:obj}) is nearly convex, and we choose to use an intuitive iterative approach to find an approximate smoothing radius.

@@

        This method is applicable to workflows that require matching data with different frequency content. 
        Here, we demonstrate that using this algorithm to match high-resolution and legacy seismic images produces better results.

        High-resolution seismic data, such as those acquired with the P-cable acquisition system, can produce very detailed images of the near subsurface \cite[]{tip}. 
        When compared to conventional seismic images, high-resolution images have a higher dominant frequency and a larger frequency bandwidth. 
        However, they usually lack low frequency content and depth coverage that is present in conventional seismic images. 
        As a result, successful interpretation of high-resolution images can be aided by matching with legacy data coverage over the same area.

@@

\subsection{Iterative method for calculating the smoothing radius: A modification}
        The algorithm previously presented works well in cases when one data set has clearly higher frequency content than the other.
        %However, this need not always be the case.
        However, in some cases, the two data sets may have similar local frequency content, but they may still need to be matched.
        We illustrate a modified version of the previous algorithm by demonstrating it on an example of multi-component seismic image registration.

@@

\section{Convergence analysis}
\inputdir{convergence}
        Since this algorithm was developed from observations and intuition based on what smoothing is physically doing, no error analysis or convergence criteria has been developed in this thesis.
        However, it is observed that this algorithm generally exhibits sublinear convergence.
        Additionally, the initial guess for what the smoothing radius should be negligibly impacts the final result.
        Figure \ref{fig:all} shows the convergence of the algorithm from equation (\ref{eq:alg}) when applied to the {\em P-cable} data set from the second example in this chapter (Figure \ref{fig:legacy,hires-agc}).
        It is evident that no matter the initial guess, the resulting convergence is relatively unaffected, and with the correct choice of step length $c$, converges in few iterations.
        After convergence, continuing iterations do not affect the final result.

        Figure \ref{fig:scalar} shows the convergence when choosing different values of $c$, the step length from Equation (\ref{eq:alg}).
        From this, it is evident that the step length is important for fast and stable convergence. 
        If too large a step length is chosen, the method does not converge to the ideal solution.
        If the step length is too small, the algorithm takes many more iterations to converge.
        With the ``correct'' step length, however, the algorithm usually converges in under 10 iterations in practice.

@@

\section{Conclusions}
        It is difficult to compare signals with differing frequency content because signals with differing frequencies are hard to correlate. 
        In this chapter, we proposed two methods of balancing frequency content between data. 
        The first one takes a theoretical approach of what we expect the data to be, and the second one takes the form of an optimization problem solved by a simple iterative algorithm. 
        This algorithm is a relatively inexpensive and effective method compared to previously proposed methods of balancing frequencies between data sets. 
        We applied these methods to examples of matching seismic images of differing resolution and for multicomponent image registration.

>>>>

\begin{abstract}
        Seismic data can experience non-stationary frequency variations caused by attenuation. 
        This problem is encountered when matching multiple data sets, such as in multicomponent image registration, because signals with differing frequency content are hard to correlate. 
        In this chapter, we introduce two methods for balancing frequency content between data sets while taking into account non-stationary frequency variations. 
        Both methods involve finding and applying a non-stationary smoothing operator to minimize the local frequency difference between data sets. 
        Numerical examples demonstrate that the proposed method improves multicomponent image registration and matching images of differing resolutions. 
\end{abstract}

\section{Introduction}
        Matching seismic data has many applications in geophysical processing methods, such as multi-component image registration, time-lapse image registration, matching well-ties to seismic data, and merging seismic data sets \cite[]{ps,fomel2003,lumley,herrera2012}.
        Typically, the workflow for matching data involves finding the optimal time shift, or amount of stretching and compressing, of one trace relative to the other that produces the greatest similarity between the two traces, as seen in dynamic time warping and local similarity scanning \cite[]{hale2013, timelapse, herrera}. 
        However, when the two signals that need to be aligned have different spectral content, their comparison can be difficult. 
        Seismic data contain non-stationary, or spatially and temporally variant, frequency content caused by attenuation. 
        This problem was discussed in application to multicomponent image registration by \cite{fomel2003}, who applied frequency balancing methods to improve registration results. 
        \cite{ltft} proposed using local time-frequency decomposition (LTFD) to balance frequencies between multicomponent data during registration. 
        However, LTFD is a relatively computationally expensive method.

        In this chapter, we propose methods for removing non-stationary frequency differences that limit the effectiveness of matching data. 
        We suggest applying either of the proposed methods to processing flows that involve matching data before attempting to find the time shift to align their signal content. 
        To balance frequency content, we use a non-stationary smoothing operator with an adjustable smoothing radius to apply to the higher frequency data set. 
        Our first approach finds the smoothing operator directly, but it is based on the primary assumption that the data can be modeled by a summation of Ricker wavelets. 
        Our second approach of finding the smoothing radius is based on understanding what the smoothing operator physically does, and takes the form of an optimization problem which is solved using an iterative method. 
        We introduce these methods and apply them to examples of merging high-resolution and conventional seismic images and multicomponent image registration.

@@

        In order to balance local frequency content, we propose smoothing the higher frequency data using a non-stationary triangle smoothing operator with an adjustable radius. 
        Here, the radius at each point is the number of samples in time that that specific data point is averaged over in a triangle weight.

        %In order to find the temporally and spatially variable smoothing radius that we need to apply to the higher frequency image to balance local frequency content with the lower frequency image, we take two approaches.
        We find the temporally and spatially variable smoothing radius to apply to the higher frequency image to balance local frequency content with the lower frequency image by taking two approaches.
        The first approach is finding the smoothing radius based on assumptions of what the data we are looking at can be represented by, and the second approach is based on understanding physically what non-stationary smoothing does to a data set.
        Both approaches work well in different situations---the first approach is less computationally expensive than the second approach, but is only applicable when the two data sets fit the assumptions that are used to calculate what the smoothing radius is.
        The second approach finds the smoothing radius in an iterative manner, but it manages to work well for any data set given to it.

@@

        This method is based off of the primary assumption that the signal can be represented by Ricker wavelets convolved with the Earth's reflectivity series.
        Because the data we are working with are seismic amplitudes, this can be a good assumption \cite[]{ricker}.

@@

        We measure local frequencies in both images and apply smoothing specified by equation~(\ref{eq:radius}) to the high-resolution image.
        Because this is only an approximation of what the smoothing radius should be under ideal conditions, we adjust the constant $12$ in the equation to achieve a better match. 
        In this example, this effectively reduces the difference between the spectral content of the images, as shown in Figure \ref{fig:hires-smooth-spec}. 
        Figure \ref{fig:freqdif,freqdif-filt} shows the difference in local frequencies before and after smoothing. 
        After smoothing, the frequency difference is minimized.

@@

        \subsection{Iterative method for calculating the smoothing radius}
        \inputdir{merge}
        The theoretical smoothing radius works in some situations, like in the first example of the next chapter, but it does not work in situations where litte overlap is present in frequency content between data sets, like in the second example of the next chapter.
        In this case, we use an iterative method to find what the smoothing radius should be that is based on the physical understanding of what smoothing is doing.

        The goal of this method is to find the temporally and spatially variable smoothing radius, $\mathbf{R}$, that minimizes the difference in local frequencies between the two data sets. 
        This can be shown in the objective function
        \begin{equation}
                \label{eq:obj}
                \min_{\mathbf{R} \in [1,N]} \Big \Vert \mathbf{F}[ \mathbf{S}_{\mathbf{R}} \mathbf{d}_h ] - 
                \mathbf{F}[ \mathbf{d}_l] \Big \Vert\;,
        \end{equation}
        where $\mathbf{S}_\mathbf{R}$ is the non-stationary smoothing operator of smoothing radius $\mathbf{R}$, $\mathbf{d}_h$ is the higher frequency data, $\mathbf{d}_l$ is the lower frequency data, $\mathbf{F}$ is the local frequency operator, and $N$ is the maximum size of the smoothing radius.
        Although smoothing is a linear operation, the smoothed data, $\mathbf{S_R d}_h$, depends non-linearly on $\mathbf{R}$. However, the objective from equation (\ref{eq:obj}) is nearly convex, and we choose to use an intuitive iterative approach to find an approximate smoothing radius.

@@

        This method is applicable to workflows that require matching data with different frequency content. 
        Here, we demonstrate that using this algorithm to match high-resolution and legacy seismic images improves the results.%produces better results.

        High-resolution seismic data, such as those acquired with the P-cable acquisition system, can produce very detailed images of the near subsurface \cite[]{tip}. 
        When compared to conventional seismic images, high-resolution images have a higher dominant frequency and a wider frequency bandwidth. 
        However, they usually lack low frequency content and depth coverage that is present in conventional seismic images. 
        As a result, successful interpretation of high-resolution images can be aided by matching with legacy data coverage over the same area.

@@

\subsection{Iterative method for calculating the smoothing radius: A modification}
        The algorithm previously presented works well in cases when one data set has clearly higher frequency content than the other.
        %However, this need not always be the case.
        However, in some cases, the two data sets may have similar local frequency content, but they might still need to be matched.
        We illustrate a modified version of the previous algorithm by demonstrating it on an example of multi-component seismic image registration.

@@

\section{Convergence analysis}
\inputdir{convergence}
        Because this algorithm was developed from observations and intuition based on what smoothing is physically doing, no error analysis or convergence criteria has been developed in this thesis.
        However, it is observed that this algorithm generally exhibits sublinear convergence.
        Additionally, the initial guess for what the smoothing radius should be negligibly impacts the final result.
        Figure \ref{fig:all} shows the convergence of the algorithm from equation (\ref{eq:alg}) when applied to the {\em P-cable} data set from the second example in this chapter (Figure \ref{fig:legacy,hires-agc}).
        It is evident that no matter the initial guess, the resulting convergence is relatively unaffected, and with the correct choice of step length $c$, converges in few iterations.
        After convergence, continuing iterations do not affect the final result.

        Figure \ref{fig:scalar} shows the convergence when choosing different values of $c$, the step length from Equation (\ref{eq:alg}).
        From this, it is evident that the step length is important for fast and stable convergence. 
        If too large a step length is chosen, the method does not converge to the ideal solution.
        If the step length is too small, the algorithm takes many more iterations to converge.
        With the ``correct'' step length, however, the algorithm usually converges in fewer than 10 iterations in practice.

@@

\section{Conclusions}
        Comparing signals with differing frequency content is difficult because signals with differing frequencies are hard to correlate. 
        In this chapter, we proposed two methods of balancing frequency content between data. 
        The first one takes a theoretical approach of what we expect the data to be, and the second one takes the form of an optimization problem solved by a simple iterative algorithm. 
        This algorithm is a relatively inexpensive and effective method compared to previously proposed methods of balancing frequencies between data sets. 
        We applied these methods to examples of matching seismic images of differing resolution and for multicomponent image registration.

### 2018-04-30 chapter-merge/paper.tex
done... can't get thesis to compile though!
thesis and presentation

    When multiple data sets are acquired over the same area using different technologies, it is likely that these data sets contain signal content from different frequency bands, which correspondingly contain unique information about the subsurface. 
    In order to utilize all available information, it may be beneficial to produce a consolidated broad-bandwidth volume that combines these data sets.
    Many previous methods of seismic data merging have been developed for the purpose of increasing the spatial coverage of the merged volume by combining data from partially overlapping areas. 
    This usually involves steps such as rebinning for data alignment, along with spectral and phase matching.
    As a result, both the initial and resultant merged images poses similar signal characteristics, most notably spectral content \cite[]{kavery,gabor,supermerge}. 
    However, previously \cite{freqmerge} are successful in applying a frequency domain merge to two separate seismic volumes over the same area to broaden the effective bandwidth.

@@

    The initial legacy and high-resolution example images are shown in Figure~\ref{fig:legacy,hires,merge2-reverse}. 
    They both underwent standard marine processing flows, and are assumed to be optimally processed.
    The images show similar structures, particularly at shallow depths, but with strikingly different resolution. 
    The main difference comes from the broader frequency bandwidth of the high-resolution image in comparison with that of the legacy image. 
    Therefore, our first step in comparing the two images is balancing their spectral content.

@@

%    After smoothing, the frequency difference is minimized.

@@

    In addition to frequency balancing, we initially attempted accounting for wavelet phase differences between data sets at this step. 
    However, we saw this had a negligible impact on the final result, so we decided not to include it in this method.

%%    \multiplot{2}{freqdif,freqdif-filt}{width=0.65\columnwidth}{Difference in local frequencies between the legacy and high-resolution images before (a) and after (b) balancing their frequency content by non-stationary smoothing.}

@@

    Since the high-resolution and legacy images contain information about the same subsurface, we can attempt to create an optimal image of this area by blending the two images together to combine the strengths of each while minimizing their weaknesses.
    We can achieve this by imposing two conditions. 
    First, the blended image should match the high-resolution image, particularly in the shallow part. 
    Second, after smoothing with the non-stationary smoothing operator, the blended image should match the legacy image. 
    We combine the two conditions together in the least-squares system
    \begin{equation}
        \label{eq:lsf}
        \left[\begin{array}{c} \mathbf{W_h} \\
                \mathbf{W_lS} \end{array}\right]\,\mathbf{b} \approx \left[\begin{array}{c} \mathbf{W_h\,h} \\
                \mathbf{l} \end{array}\right]\;,
    \end{equation}
    where $\mathbf{h}$ denotes the high-resolution image, $\mathbf{l}$ is the legacy image, $\mathbf{b}$ is the desired blended image, $\mathbf{W_h}$ and $\mathbf{W_l}$ are the diagonal weighting matrices for the high-resolution and legacy images, respectively, and $\mathbf{S}$ is the non-stationary smoothing specified by equation (\ref{eq:rad}). 
    The formal solution of the least-squares problem~(\ref{eq:lsf}) is
    \begin{eqnarray}
        \mathbf{b} & = & \left(\mathbf{W_h}^2 + \mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\right)^{-1}\,\left(\mathbf{W_h}^2\,\mathbf{h}+\mathbf{S}^T\,\mathbf{W_l}\mathbf{l}\right)\;.
        \label{eq:inv}
    \end{eqnarray}

@@

    The weights, $\mathbf{W_h}$ and $\mathbf{W_l}$, are applied to the images to bring out the desired qualities from each image. 
    For example, since we prefer the high-resolution image in the shallow section, we weight it stronger there and gradually taper the weight to preference the legacy image with depth. 
    In addition, we estimate the legacy weight, $\mathbf{W_l}$, to balance the legacy image's amplitudes with respect to the high-resolution image. 
    The specific values we used for the weights are shown in Figure \ref{fig:hweight,lweight-reverse}.

@@

    There is a definite separation in frequency content when comparing the legacy and high-resolution images (Figure \ref{fig:nspectra2}). 
    Because there is not much overlap in frequency bandwidth, balancing their spectral content is challenging. 
    In addition, a primary assumption made in deriving the theoretical smoothing radius (equation \ref{eq:rad}) is that the signal is modeled by a summation of Ricker wavelets, which may not be a correct assumption. 
    As a result, additional steps must be taken beyond applying the smoothing specified by equation~(\ref{eq:rad}) to ensure matching frequency content. 
    \plot{nspectra2}{width=0.75\columnwidth}{The spectral content of the entire image display of the legacy (red dashed), high-resolution (blue dotted), and resultant merged (magenta solid) images for the second data set.}

@@

%\onecolumn
%
%\bibliographystyle{seg}
%\bibliography{SEG,merge}

>>>>

    When multiple data sets are acquired over the same area using different technologies, it is likely that these data sets contain signal content from different frequency bands, which correspondingly contain unique information about the subsurface. 
    In order to utilize all available information, it may be beneficial to produce a consolidated broad-bandwidth volume that combines these data sets.
    Many previous methods of seismic data merging have been developed for the purpose of increasing the spatial coverage of the merged volume by combining data from partially overlapping areas. 
    This usually involves steps such as rebinning for data alignment, along with spectral and phase matching.
    As a result, both the initial and resultant merged images poses similar signal characteristics, most notably spectral content \cite[]{kavery,gabor,supermerge}. 
    However, previously \cite{freqmerge} were successful in applying a frequency domain merge to two separate seismic volumes over the same area to broaden the effective bandwidth.

@@

    The initial legacy and high-resolution example images are shown in Figure~\ref{fig:legacy,hires,merge2-reverse}. 
    They both underwent standard marine processing flows and are assumed to be optimally processed.
    The images show similar structures, particularly at shallow depths, but with strikingly different resolution. 
    The main difference comes from the broader frequency bandwidth of the high-resolution image in comparison with that of the legacy image. 
    Therefore, our first step in comparing the two images is balancing their spectral content.

@@

    %After smoothing, the frequency difference is minimized.

@@

    In addition to frequency balancing, we initially attempted to account for wavelet phase differences between data sets at this step. 
    However, we saw this had a negligible impact on the final result, so we decided not to include it in this method.

    % \multiplot{2}{freqdif,freqdif-filt}{width=0.65\columnwidth}{Difference in local frequencies between the legacy and high-resolution images before (a) and after (b) balancing their frequency content by non-stationary smoothing.}

@@

    Because the high-resolution and legacy images contain information about the same subsurface, we can attempt to create an optimal image of this area by blending the two images together to combine the strengths of each while minimizing their weaknesses.
    We can achieve this by imposing two conditions. 
    First, the blended image should match the high-resolution image, particularly in the shallow part. 
    Second, after smoothing with the non-stationary smoothing operator, the blended image should match the legacy image. 
    We combine the two conditions together in the least-squares system
    \begin{equation}
        \label{eq:lsf}
        \left[\begin{array}{c} \mathbf{W_h} \\
                \mathbf{W_lS} \end{array}\right]\,\mathbf{b} \approx \left[\begin{array}{c} \mathbf{W_h\,h} \\
                \mathbf{l} \end{array}\right]\;,
    \end{equation}
    where $\mathbf{h}$ denotes the high-resolution image, $\mathbf{l}$ is the legacy image, $\mathbf{b}$ is the desired blended image, $\mathbf{W_h}$ and $\mathbf{W_l}$ are the diagonal weighting matrices for the high-resolution and legacy images, respectively, and $\mathbf{S}$ is the non-stationary smoothing specified by equation (\ref{eq:rad}). 
    The formal solution of the least-squares problem~(\ref{eq:lsf}) is
    \begin{eqnarray}
        \mathbf{b} & = & \left(\mathbf{W_h}^2 + \mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\right)^{-1}\,\left(\mathbf{W_h}^2\,\mathbf{h}+\mathbf{S}^T\,\mathbf{W_l}\mathbf{l}\right)\;.
        \label{eq:inv}
    \end{eqnarray}

@@

    The weights, $\mathbf{W_h}$ and $\mathbf{W_l}$, are applied to the images to bring out the desired qualities from each image. 
    For example, because we prefer the high-resolution image in the shallow section, we weight it more significantly there and gradually taper the weight to preference the legacy image with depth. 
    In addition, we estimate the legacy weight, $\mathbf{W_l}$, to balance the legacy image's amplitudes with respect to the high-resolution image. 
    The specific values we used for the weights are shown in Figure \ref{fig:hweight,lweight-reverse}.

@@

    There is a definite separation in frequency content when comparing the legacy and high-resolution images (Figure \ref{fig:nspectra2}). 
    Because of little overlap in frequency bandwidth, balancing their spectral content is challenging. 
    In addition, a primary assumption made in deriving the theoretical smoothing radius (equation \ref{eq:rad}) is that the signal is modeled by a summation of Ricker wavelets, which may not be a correct assumption. 
    As a result, additional steps must be taken beyond applying the smoothing specified by equation~(\ref{eq:rad}) to ensure matching frequency content. 
    \plot{nspectra2}{width=0.75\columnwidth}{The spectral content of the entire image display of the legacy (red dashed), high-resolution (blue dotted), and resultant merged (magenta solid) images for the second data set.}

@@
